Verification of Stencil Computations through Spatial Specifications

### 2016-07-03 paper.tex
abstract tweak

\begin{abstract}
Verifying the correctness of numerical computations relies on a specification of their behaviour.
A natural way to do this would be in terms of the original mathematical model but this approach yields specifications which are highly decoupled from the code.
Checking the correctness of code which implements a discrete approximation of such specifications is extremely challenging.
Instead we have been investigating intermediate
  systems of specification and verification between lower-level
  aspects (\eg{}, out-of-bounds errors) and full correctness
  based on a numerical model. In this paper, we focus on
  \emph{stencil computations}---a common idiom in numerical code, but
  one which is error-prone due to fine-grained indexing errors.
%
We describe a stencil specification language which can be directly embedded as annotations in source code, along with an inference and checking procedure.
%
We evaluate our language against a corpus of numerical Fortran code, and show
  that precise specifications can be given to $X\%$ of identifiable
  stencil computations, with a mean ratio of $Y:Z$
  specification-to-program code and that the vast majority of stencil computations have a simple, regular, static shape.
%
This paper details our stencil
  specification language, its static semantics, inference, checking,
  and program synthesis procedures, our implementation, and our
  evaluation study.
%
We provide an implementation of stencil inference and validation in \emph{Camfort}, an open-source program analysis and refactoring tool.
\end{abstract}

>>>>

\begin{abstract}
  Verifying the correctness of numerical computations relies on first
  giving a specification of their behaviour. In many cases, a
  numerical computation is derived from an underlying mathematical
  model, but this is often difficult to use as a specification as it
  is highly decoupled from the implementation. We have been studying
  specification techniques in middle ground between low-level and
  high-level specifications for numerical code. In this paper, we
  focus on \emph{stencil computations}---a common idiom in numerical code, but
  one which is error-prone due to fine-grained indexing errors. We
  hypothesise that in practise, stencil computations tend to have a
  regular shape which is amenable to static analysis and simple
  specification. We describe a abstract specification language for
  stencil computations that can be directly embedded as annotations in
  source code, along with an inference and checking procedure. We
  evaluate our language against a corpus of numerical Fortran code,
  and show that precise specifications can be given to roughly half of
  the identifiable stencil computations, and that the vast majority of
  stencil computations indeed have a simple, regular, static
  shape. This paper details our stencil specification language, its
  static semantics, inference, checking, and program synthesis
  procedures, our implementation, and our evaluation study. We provide
  an implementation of stencil inference and validation in Camfort, an
  open-source program analysis and refactoring tool.
\end{abstract}
